### 2016-05-13 paper/paper.tex
s/TLSv/TLS /

TODO: how does Peercoin make sure other mint?ers can't steal the coinstake
transaction? Is it signed by the coinstake kernel, or does the coinstake kernel
include the merkle root of transactions somehow?

@@

@@

There are several methods victim websites can use to defend themselves from
DDoSCoin miners. First, websites can simply disable TLS 1.2 entirely, and only
support earlier versions such as TLS 1.0~\cite{rfc2246} and TLS
1.1~\cite{rfc4346}. While older versions of
TLSv1.0 clients may still be vulnerable to the BEAST attack~\cite{beast}, most
modern clients have mitigations for this attack, and it likely remains the
safest short-term defense against DDoSCoin. The downside of disabling support
for TLSv1.2 is losing the ability to negotiate authenticated encryption cipher
modes with clients, which may decrease performance of implementations that have
hardware acceleration for such modes.

Alternatively, web servers can disable cipher modes that involve signatures from
the server. This would remove support for forward secure cipher suites, meaning
that as long as the server's private key is accessible, any previously recorded
TLS connections can be decrypted. We note that the current drafts of TLSv1.3
propose to remove non-forward secure cipher suites entirely, possibly making it
more difficult to defend against DDoSCoin in TLSv1.3.

>>>>

%TODO: how does Peercoin make sure other mint?ers can't steal the coinstake
%transaction? Is it signed by the coinstake kernel, or does the coinstake kernel
%include the merkle root of transactions somehow?

@@

\label{sec:pay-to-ddos}

@@

There are several methods victim websites can use to defend themselves from
DDoSCoin miners. First, websites can simply disable TLS 1.2 entirely, and only
support earlier versions such as TLS 1.0~\cite{rfc2246} and TLS
1.1~\cite{rfc4346}. While older versions of
TLS 1.0 clients may still be vulnerable to the BEAST attack~\cite{beast}, most
modern clients have mitigations for this attack, and it likely remains the
safest short-term defense against DDoSCoin. The downside of disabling support
for TLS 1.2 is losing the ability to negotiate authenticated encryption cipher
modes with clients, which may decrease performance of implementations that have
hardware acceleration for such modes.

Alternatively, web servers can disable cipher modes that involve signatures from
the server. This would remove support for forward secure cipher suites, meaning
that as long as the server's private key is accessible, any previously recorded
TLS connections can be decrypted. We note that the current drafts of TLS 1.3
propose to remove non-forward secure cipher suites entirely, possibly making it
more difficult to defend against DDoSCoin in TLS 1.3.
